Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-08-17 Docs/Paper/LaTex/template.tex
Added modifications made in docx to LaTex

\subsection{\textcolor{Red}{Multi-core ESBMC with OpenMP using Binary Search}}
The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.

Since OpenMP only returns from a parallelized loop when every forked thread finishes, some processor could remain idle for some time.
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
	\caption{gestaucht}
	\label{fig2}
\end{figure}
So the first approach was to remove the Idle time from the parallel loops by creating workers inside the threads to always execute the next step until a violation is find. At first though it seemed to be a great improvement but as ESBMC executes almost the same time the steps, there was almost no optimization.

The most optimized approach used was to use a parallelized binary search to reduce the complexity of the tasks. So was made a controller to return the best step to execute in order to reduce the domain as maximum as possible. This is done by dividing the domain in chunks and than returning the middle of the biggest chunk existent, and creating two new chunks.
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
	\caption{gestaucht}
	\label{fig2}
\end{figure}

To exemplify, given a problem of domain 1 to 20, first we create an initial chunk  1 – 20. When the next available core asks for a step to execute, the controller gets the biggest chunk which in this case is 1 – 20, divide it by 2, creates two new chunks and return the middle of the original chunk. So it would be 2 new chunks 1 – 9 and 11 – 20, and the returned step will be 10. Additional checks are needed to avoid the creation of empty or invalid chunks.
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=75px]{Image/Fig4.png}
	\caption{gestaucht}
	\label{fig2}
\end{figure}

Additionally, since there will be a gap between the steps, produced by the customized binary search algorithm, it is possible that a lot of steps will not be needed to execute. For instance, on the example above, if a step 10 return false, it is obvious that every step after 10 will also be a violation. On the other hand, if the same step was successful, we can assume that every step before 10 will also be a valid.

That said, was implemented in the controller a method to discard unnecessary steps by removing or shrinking existing chunks. It made a very big impact in the calculation time. However a step can be running and not be needed anymore, in this case the binary algorithm kills the forked  process and starts a new one.
\begin{lstlisting}
01. GetNextStep(){
02.  int largestChunk = -1;
03.  chunk largest;
04.  for each(chunk in chunks){
05.     if(chunk.right - chunk.left > largestChunk){
06.           largestChunk = chunk.right - chunk.left;
07.           largest = chunk;
08.     }
09.   }	
10.   chunks.remove(largest);	
11.   int median = largest.left + floor((largest.right - largest.left) / 2)
12.   if(median > 0){
13.      if(largest.right - largest.left > 1)
14.         chunks.add(new chunk(largest.left, median - 1));	
15.      if(largest.right != largest.left)
16.         chunks.add(new chunk(median + 1, largest.right);
17.    }
18.   return median;
19. }
\end{lstlisting}
 The execution is made by executing the procedure described pseudocode before and then starting the process of the ESBMC to execute the returned step.
While the step is being executed the algorithm query the controller to check if this step is still needed. If not, the ESBMC instance is killed and the worker is free to start another step.

\begin{lstlisting}
01. step = controller.GetNextStep();
02. int pid = ExecuteStep(step);
03. while(isRunning(pid)){
04.   if(!controller.isNeeded(step))
05.    kill(pid);
06. }     
\end{lstlisting}

@@

\textcolor{Red}{Os resultados obtidos destacam as ferramentas vZ e ILP.
Vz resolveu corretamente 4 de 7 algoritmos, teve um falso positivo no algoritmo RC6, seu resultado mais lento comparado a ILP Foi no algoritmo Patricia onde este foi 3.33 vezes mais rápido, vZ retornou dois TO(Time OUT) em Fuzzy e Mars.}

\textcolor{Red}{Em contrapartida, ILP Resolveu corretamente 6 de 7 algoritmos, não teve falso positivo, o tempo de resolucao do problema é maior quando comparamos com ILP/vZ e menor quando comparado com ILP/ESBMC, isso o coloca como uma ferramenta otima em resolucao e intermediaria no quesito tempo.  }

\textcolor{Red}{A unica tecnica capaz de resolver todos os benchmarks foi GA, entretanto, a precisão não foi satisfatoria, a taxa de erro variou entre -37.6\% até 29.0\%.}

\textcolor{Red}{Todas as versões do ESBMC paralelo obtiveram melhores resultados do que no modo sequencial, destaca-se a versão binaria descrita na secao 2.5, o desempenho se torna cada vez melhor quando se aumenta o numero de nós e arestas. o algoritmo Clustering quando processado pelo ESBMC paralelo obteve um desempenho 3.13 vezes melhor do que ILP, seu tempo de 207 segundos é muito proximo do tempo de solucao do Vz que é de 109 segundos. }

@@

\textcolor{Red}{A Tabela 2 mostra avancos na paralelizacao de algoritmos para problemas de particionamento, ESBMC obteve excelentes resultados quando executado de modo paralelo, as ferramentas vZ e ILP ainda se comportam de forma precisa frente ao ESBMC.}

>>>>

\subsection{\textcolor{Red}{Multi-core ESBMC with OpenMP using Binary Search}}
\textcolor{Red}{The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.

Since OpenMP only returns from a parallelized loop when every forked thread finishes, some processor could remain idle for some time.}
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel.png} 
	\caption{gestaucht}
	\label{fig2}
\end{figure}
\textcolor{Red}{Consequently, the first approach aims to remove the idle time from the parallel loops, by creating workers inside the threads to execute the next step until a violation is found. This approach could potentially lead to a great improvement, but as ESBMC executes the sequential steps almost at the same time, the processor does not remain idle for a longer period and thus there is almost no optimization

The most optimized approach applies a parallelized binary search to reduce the amount of steps executed  in order to find the most optmized solution. As a result, the controller is designed to return the best step to execute so that the number of steps are reduced as maximum as possible. The parallelized binary search accomplishes this by splitting the domain into intervals and then returning the middle of the largest interval, which thus creates two new intervals.}
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{Image/esbmc-parallel-Controler.png} 
	\caption{gestaucht}
	\label{fig2}
\end{figure}

\textcolor{Red}{As example, given a problem of domain 1 to 20, firstly we create an initial interval from 1 to 20. When the next available core asks for a step to execute, the controller gets the biggest interval, which in this case is 1 – 20, divide it by 2, creates two new intervals and return the middle of the original interval. Therefore, there would be 2 new intervals, one from 1 to 9 and another one from 11 to 20, and the returned step would be 10. The controller also checks when an interval has less than two elements to avoid the creation of empty or invalid intervals. }
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=75px]{Image/Fig4.png}
	\caption{gestaucht}
	\label{fig2}
\end{figure}

\textcolor{Red}{Additionally, since there is a gap between the steps, produced by the customized binary search; in particular, there might be several steps are not executed. For instance, in the example above, if step 10 returns false, then one can conclude that all steps after 10 is false as well. However, if the same step 10 is true, we can assume that all steps before 10 is true as well.

As a result, a method to remove unnecessary steps is implemented in the controller by removing or shrinking existing intervals. This approach leads to a high impact in the verification time. However, if a step is running and is not needed anymore, the worker kills the forked process and starts a new one.}
\begin{lstlisting}
01. GetNextStep(){
02.  int largestChunk = -1;
03.  chunk largest;
04.  for each(chunk in chunks){
05.     if(chunk.right - chunk.left > largestChunk){
06.           largestChunk = chunk.right - chunk.left;
07.           largest = chunk;
08.     }
09.   }	
10.   chunks.remove(largest);	
11.   int median = largest.left + floor((largest.right - largest.left) / 2)
12.   if(median > 0){
13.      if(largest.right - largest.left > 1)
14.         chunks.add(new chunk(largest.left, median - 1));	
15.      if(largest.right != largest.left)
16.         chunks.add(new chunk(median + 1, largest.right);
17.    }
18.   return median;
19. }
\end{lstlisting}
\textcolor{Red}{The algorithm above describes how the customized binary search calculates and returns the step to be executed. From line 4 to 9 the algorithm finds the biggest interval. Then from the line 10 the biggest interval is removed and the median is calculated in the line 11. Then 2 new intervals are created, the left side on line 14 and the right side on the line 16. At the end, the median is returned.}

\begin{lstlisting}
01. step = controller.GetNextStep();
02. int pid = ExecuteStep(step);
03. while(isRunning(pid)){
04.   if(!controller.isNeeded(step))
05.    kill(pid);
06. }     
\end{lstlisting}
\textcolor{Red}{The algorithm above describes how the worker starts and monitors the ESBMC instances. The algorithm starts by retrieving the step to execute from the controller (line 1) , starts the instance of ESBMC and get the process id from the forked process (line 2). While the step is being executed, the controller checks whether this step is still needed (line 4). If not, then the ESBMC instance is killed (line 5) and the worker is free to initiate another step.}

@@

\textcolor{Red}{The results obtained that standout were the ILP and vZ.
Vz solved correctly 4 of 7 algorithms, got an false positive in the algorithm RC6, the slowest result compared with ILP was Patricia that was 3.33 times faster, vZ returned two TO (time outs) in Fuzzy and Mars.}

\textcolor{Red}{In contrast, ILP solved correctly 6 of 7 algorithms, do not had any false positive, the resolution time is bigger compared with vZ and lower compared with ESBMC, it shows that ILP is optimized to solve problems but has an average resolution time.}

\textcolor{Red}{The only technique aqble to solve all algorithms was GA, however it's precision was not satisfatory, it had error rate between -37.6\% and 29.0\%.}

\textcolor{Red}{All versions of parallel ESBMC got better results compared with the sequential approach, stands out the binary version described on the section 2.5, the performance get better as the number of nodes and edges get bigger. The clustering algorithm when processed by the parallel ESBMC had 3.13 better performance than ILP, it`s time was 207 seconds and is very cloe to the solution of vZ that is 109 seconds.}

@@

\textcolor{Red}{The table 2 shows the advances in the parallelization of algorithms of partitioning problems, ESBMC had great results when executed in parallel, the vZ and ILP had precise results as ESBMC.}
